---
title: "Assignmentrepre"
author: "Fabricio Dujardin"
date: "7/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data

```{r 1 QUESTION}

library(data.table)
library(lubridate)

data <- data.table(read.csv("activity.csv"))
str(data)
data[,date:= ymd(date)]


```

#What is mean total number of steps taken per day?
##Calculate the total number of steps taken per day
##Make a histogram of the total number of steps taken each day
##Calculate and report the mean and median of the total number of steps taken per day

```{r 2 QUESTION, echo=TRUE}
names(data)
stepday<-data[,sum(steps,na.rm=T), by=date]
stepday<- stepday[,V1:= {V1[is.na(V1),] <- 0}
stepday
library(ggplot2)

g <- ggplot(stepday, aes(V1)) 
g + geom_histogram()

stepmean <- data[,Mean:=mean(steps,na.rm=T), by=date][]
stepmean
stepmedian <- data[,median(steps,na.rm=T), by=date][]
stepmedian
```

#What is the average daily activity pattern?

##Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
##Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r QUESTION 3, echo=TRUE}



```


#imputing missing values

#Note that there are a number of days/intervals where there are missing values (coded as ð™½ð™°). The presence of missing days may introduce bias into some calculations or summaries of the data.

#Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with ð™½ð™°s)
#Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.
#Create a new dataset that is equal to the original dataset but with the missing data filled in.
#Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?


```{r QUESTION 4, echo=TRUE}

data[is.na(steps),.N,by=date]

replacement<-data[,mean(steps,na.rm=T),by=interval]

#tobereplaced<- function(x){}

#data[is.na(steps),lapply(.SD,tobereplaced)]

data[is.na(steps),]$stepsnew <- data[is.na(steps),Mean]
```
One day has 60minutes times 24 hours = 1440 min, divided by 5 minutes we get 288 times 5 minutes in one day. We can see that there is 288 rows of NAs for the following dates. Therefore it is not possible to get the mean of the day for the 5 min intervals. I would need to take the average of the intervals of each day in order to replace each interval. Which would not be correct to my eyes, but for sake of computation it has been done.